---
title: "Portfolio Efficient Frontier -- Group 15"
author: "Garrett Stephens, Sabrina Rodriguez, Mikayla Williams, Jeffri Behrens"
date: "12/10/2022"
output:
  pdf_document: default
  word_document: default
---

## Portfolio Efficient Frontier

Below is the Efficient Frontier based on the returns of Nasdaq listed stocks 
from January 2000 to December 2009. The graph depicts the frontier from a 4% 
to a 7.9% expected portfolio return.

```{r pressure0, message=FALSE, echo=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(RMySQL)
library(knitr)
library(ggplot2)
```

```{r pressure1, echo=FALSE}

con <- dbConnect(RMySQL::MySQL(), dbname='nasdaq',
                 username='root',password='root')
# dbListTables(con)

query <- paste0("select * from portfolio; ")

runquery <- dbSendQuery(con,query)
df <- fetch(runquery, n=-1)

# dbDisconnect(con)

x <- df[1]
y <- df[2]

ggplot() +
  geom_line(data=df,mapping=aes(x=expRisk,y=expReturn),color='red')+
  geom_line(data=df,mapping=aes(x=expRisk,y=expReturn),color='red')+
  labs(x='Portfolio Expected Risk',y='Portfolio Expected Return',title = 'Portfolio Efficient Frontier')
```
** The Expected Return is in percentage ( % ) units; The Expected Risk is the Portfolio Standard Deviation. 

## Commentary

The Efficient Frontier visualizes the potential return someone can expect given
their risk tolerance. As one's risk tolerance increases, so does their 
expected return -- greater risk exposes you to greater reward (or loss) as these
stock are much more volatile. A portfolio above this line is impossible because 
the efficient frontier and the area below it represents the feasible region of 
stock compositions. An investor would desire to be along the efficient line
because a portfolio that experiences the same risk but is far from the line can 
be achieving greater returns. 

## Data Points of the Efficient Frontier

The Points of the above graph is available below.

```{r pressure2, echo=FALSE}
df
```
